\documentclass[12pt]{article}
\usepackage{amsmath, amsthm,graphics,setspace,graphicx,color}

\begin{document}

\begin{large}
\noindent Math 1023, Taylor Polynomial Lab
\end{large} \newline

\noindent For each exercise involving Desmos graphs, take a screen shot of your work (both the equations and the graphs). \newline

\noindent Only do one exercise at a time. Don’t try to put all the exercises in one screen shot. \newline

\noindent Submit a single PDF with your work and collection of screenshots. \newline

\noindent Do not forget to put your name(s) in the filename as well as in your document. \newline

\noindent (Ex: Smith\_Jones\_lab3.pdf)

\begin{enumerate}
	\item Construct the degree 0, 1, 2, 3, \& 4 Maclaurin polynomials for the function 
\begin{equation}
	\displaystyle f(x) = e^{bx}.
\end{equation}  Show your derivation and explicitly write each of your polynomials.

 
	\begin{enumerate}
		\item Using the Desmos Graphing Calculator, https://www.desmos.com/calculator, create a plot of 
$y=e^{bx} $ and the Maclaurin polynomials that you have constructed. 


		\item Consider the case where $b=2$ and thus
\begin{equation}
	f(x)=e^{2x}.
\end{equation}
 Use each of your polynomials in your Desmos graph to approximate $f(0.2)$ using 4 digits to the right of the decimal point, and give the magnitude of the error of each approximation, 
\begin{equation}
	|\textrm{Error}| = |f(0.2) - \textrm{approximation}|.
\end{equation}

		\item What can you conclude about the accuracy of your approximations as the polynomial degrees increase?
		\end{enumerate}
	
	
\pagebreak	

	\item Construct the degree 1, 2, 3, \& 4 Maclaurin polynomials for the function 
\begin{equation}
	g(x) = \ln(1+bx).
\end{equation}

	\begin{enumerate}
		\item Using the Desmos Graphing Calculator create a plot of $$\displaystyle y= \ln(1+bx)$$ and the Maclaurin polynomials that you have constructed. 
		\item Consider the case where $b=2$ and thus
\begin{equation}
	g(x)=\ln(1+2x).
\end{equation}
Use each of your polynomials in your Desmos graph to approximate $\displaystyle g(0.3)$ using 4 digits to the right of the decimal point, and give the magnitude of the error of each approximation,
\begin{equation}
	|\textrm{Error}| = |g(0.3) - \textrm{approximation}|.
\end{equation}
		\item For what $x$ values is this approach valid?  Describe what you observe in your graphs regarding the $x$ values outside of this region versus the $x$ values inside of this region.


	\end{enumerate}		
	
	
	
\end{enumerate}




\end{document}